### 2017-01-11 doc/manuscript.Rmd
Included citation for DAGitty (or link)

Covariates were selected based on the previous literature, from directed acyclic
graph [@Greenland1999a] recommendations (see `r cite_f('dag_is')` and `r cite_f('dag_bcf')`), and from 
QIC. `r cite_t('tab_qic')` shows the covariates compared using QIC.
While the final GEE model selected as best fitting differed between insulin
sensitivity and beta-cell function measures, the differences in QIC values were
less than 10 between many of the models, suggesting similar fit. As such, we selected
the model that had the fewest covariates and that had similar fit between the
outcome measures ({{##}}). The final GEE model was adjusted for {{covariates}}.
After scaling, log-transforming, and exponentiating, the GEE estimates are 
interpreted as an expected percent difference in the outcome variable for every 
standard deviation (SD) increase in the predictor variable given the covariates 
are held constant (including time). Lastly for the GEE models, we tested for an interaction with 
sex, ethnicity, or time by the predictor term for each outcome variable.

>>>>

Covariates were selected based on the previous literature, from directed acyclic
graph [@Greenland1999a] recommendations (using the DAGitty software
[@Textor2011a], http://dagitty.net/; see `r cite_f('dag_is')` and `r cite_f('dag_bcf')`), and from
QIC. `r cite_t('tab_qic')` shows the covariates compared using QIC.
While the final GEE model selected as best fitting differed between insulin
sensitivity and beta-cell function measures, the differences in QIC values were
less than 10 between many of the models, suggesting similar fit. As such, we selected
the model that had the fewest covariates and that had similar fit between the
outcome measures ({{##}}). The final GEE model was adjusted for {{covariates}}.
After scaling, log-transforming, and exponentiating, the GEE estimates are 
interpreted as an expected percent difference in the outcome variable for every 
standard deviation (SD) increase in the predictor variable given the covariates 
are held constant (including time). Lastly for the GEE models, we tested for an interaction with 
sex, ethnicity, or time by the predictor term for each outcome variable.
